---
title: "Problem Set 2"
author: "Your Name"
date: "`r Sys.Date()`"
output: github_document
---

```{r setup, include=FALSE, message=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE, collapse = TRUE)
# Load all necessary packages for the problem set
library(readr)
```

## 📊 The Challenge: The Global Widget Sales Dataset

**Estimated Time:** 60-75 minutes

You've have been hired as a data analyst role and are  responsible for a dataset of **500 records**. Your task is to investigate and prepare this dataset for a predictive model that will forecast future sales. This assignment will test your skills in advanced exploratory data analysis (EDA), robust data cleaning, and sophisticated feature engineering.

First, let's load the dataset.

```{r}
global_sales <- read_csv("ps2_sales_data.csv")
```

### Part 1: The Data is Dirty

You discover the dataset has inconsistencies that could lead to inaccurate analysis. Before moving forward, you need to apply robust data cleaning techniques.

**Question 1.1:** First, calculate the average `units_sold` by `product_category` without any cleaning. Then, use a function from `stringr` to standardize `product_category` into a single, consistent format and recalculate the averages. Compare the results to demonstrate why data cleaning matters.

```{r}
# Your code for Question 1.1 here
```

**Question 1.2:** The `sale_date` column is already in a date format, but for a different type of analysis, you need to create two new columns: `sale_month` (a number from 1-12) and `sale_day_of_week` (the full name of the day, e.g., "Monday"). Use functions from the `lubridate` package to extract this information.

```{r}
# Your code for Question 1.2 here
```

**Short Answer:**

Explain why it is critical for a predictive model to have a standardized `product_category` column rather than using the raw, inconsistent strings. Provide a brief example of how a model might be misled by the uncleaned data.

### Part 2: Initial Investigation & Anomaly Detection

Your second task is to explore the data and look for anomalies. A good starting point is to visualize the relationship between key variables. You'll also use a statistical method to identify potential outliers in sales data.

**Question 2.1:** Create a scatter plot visualizing the relationship between `marketing_spend` (x-axis) and `units_sold` (y-axis). Add a linear regression trend line and facet the plot by `region`. What insights can you gain about the regional effectiveness of marketing?

```{r}
# Your code for Question 2.1 here
```

**Question 2.2:** Using the `sale_day_of_week` variable you created in Part 1, calculate the average `units_sold` by day of the week and create a bar plot to visualize this pattern. What pattern emerges regarding sales throughout the week?
```{r}
# Your code for Question 2.2 here
```


**Question 2.3:** Use a box plot to visually identify any outliers in the `units_sold` variable. Then, calculate the Z-score for each observation. According to the Z-score method, any value with an absolute Z-score greater than 3 is considered an extreme outlier. How many extreme outliers do you find?

```{r}
# Your code for Question 2.3 here
```

**Short Answer:**

Compare the outliers identified by the box plot versus the Z-score method. Why might they differ? Which method would you prefer for this dataset, and why?

### Part 3: Engineering for Insight

Your manager wants you to formally model the day of week patterns you saw in `2.2`. Your task is to apply **feature engineering** to create a new binary variable to capture these patterns

**Question 3.1:** Create a new variable that captures the weekly pattern 

  - *Hint:* It should be a binary variable that relies on your previous insights.

```{r}
# Your code for Question 3.1 here
```

**Question 3.2:** What is the average `units_sold` when splitting by your new variable? What does this new feature reveal about sales patterns?

```{r}
# Your code for Question 3.2 here
```

**Short Answer:**

Explain why creating your new binary variable is more powerful for a predictive model than using the raw `sale_date` column directly.

### Part 4: Feature Engineering with Interaction Terms

Based on your initial investigation in Part 2, you noticed that marketing spend seems to have a different effect across regions. Create an **interaction term** that captures this effect for the region where you think marketing spend has the biggest impact

**Question 4.1:** Calculate and print the correlation between your new **interaction term** and `units_sold`.

```{r}
# Your code for Question 4.1 here
```

**Short Answer:**

What did you learn from comparing the correlation of your new **interaction term** with `units_sold` versus the unconditional correlation of `marketing_spend` with `units_sold`? What does this reveal about feature engineering?

### Part 5: Synthesis and Conclusion

**Question 5:** Based on your analysis in Parts 1-4, synthesize your findings and write a brief summary of the key insights you would present to the sales team.

**Short Answer:**